Modelling the emergence of whisker barrels

### 2019-12-17 paper/briefpaper/brief.tex
Adds citation in intro

Barrel formation requires afferent input from whisker stimulation and thalamic calcium waves \citep{anton-bolanos_prenatal_2019}, and depends on a complex network of axon guidance molecules such as ephrin-A5 and A7 and adhesion molecules such as cadherin-6 and 8 \citep{miller_epha7-ephrin-a5_2006}.
This network is orchestrated by interactions between morphogens Fgf8 and Fgf17 and transcription factors Emx2, Pax6, Sp8, and Coup-tf1 \citep{shimogori_fibroblast_2005}, which are expressed in gradients that mark orthogonal axes and can be manipulated to stretch, shrink, shift, and even duplicate barrels \cite{assimacopoulos_fibroblast_2012}.
% Removed ref: ,bishop_regulation_2000 after ..Coup-tf1

>>>>

Barrel formation requires afferent input from whisker stimulation and thalamic calcium waves \citep{anton-bolanos_prenatal_2019}, and depends on a complex network of axon guidance molecules such as ephrin-A5 and A7 and adhesion molecules such as cadherin-6 and 8 \citep{vanderhaeghen_mapping_2000,miller_epha7-ephrin-a5_2006}.
This network is orchestrated by interactions between morphogens Fgf8 and Fgf17 and transcription factors Emx2, Pax6, Sp8, and Coup-tf1 \citep{shimogori_fibroblast_2005}, which are expressed in gradients that mark orthogonal axes and can be manipulated to stretch, shrink, shift, and even duplicate barrels \cite{assimacopoulos_fibroblast_2012}.
% Removed ref: ,bishop_regulation_2000 after ..Coup-tf1
